\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-24 paper.tex
Remove useless subtopic

Al-Fagih et al. presented\cite{DataPrice} $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is approximately an exponential function of $P_r$. We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq. (\ref{payoff}), then we can find out the Nash Equilibrium of repeated game.

\subsubsection{Numerical Example}
To evaluate the behavior of the model we presented, first, we would express the function of $P_s$ and $C_{maintain}$ as functions of $P_r$ respectively. Therefore, the sum of subscription fee of all subscriber can be expressed as

>>>>

Al-Fagih et al. presented\cite{DataPrice} the quality of data $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is approximately an exponential function of $P_r$. We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq. (\ref{payoff}), then we can find out the Nash Equilibrium of repeated game.

To evaluate the behavior of the model we presented, first, we would express the function of $P_s$ and $C_{maintain}$ as functions of $P_r$ respectively. Therefore, the sum of subscription fee of all subscriber can be expressed as
